\documentclass[a5paper,11pt]{memoir}    
\usepackage{dramatist,etoolbox,enumitem, hyperref}
\usepackage[latin]{babel}
\usepackage[margin=.8in]{geometry}

\usepackage{marginnote}

\makeatletter
\patchcmd{\@mn@@@marginnote}{\begingroup}{\begingroup\@twosidefalse}{}{\fail}
\reversemarginpar
\makeatother

\pagestyle{empty}
\makeatletter
\renewenvironment{drama}
  {\if@lnpa
   \PackageWarning{dramatist}{\lnpwarning{a}}
   \fi
   \if@lnps
   \PackageWarning{dramatist}{\lnpwarning{s}}
   \fi
   \begin{itemize}[labelwidth=\speakswidth,leftmargin=!]} 
  {\end{itemize}}
  
\renewcommand{\casttitlename}{Characters}
\patchcmd{\speaker}{\item[#1\speaksdel]}{\item[\speaksfont#1]}{}{}
\patchcmd{\@character}{\item[#1\speaksdel]}{\item[\speaksfont#1]}{}{}
  \makeatother

\newenvironment{pc}[1]
	{ \speaker{#1}\raggedright\itshape}
	{}

\newenvironment{pct}[3]
{ \speaker{#1}\marginnote{\href{#2}{\raggedleft\tiny #3}}\itshape}
{}
	
\newenvironment{player}[1]
	{ \speaker{#1}}
	{}

\let\cleardoublepage=\clearpage % removes the blank page after the title page

\setlength{\CharWidth}{.8\textwidth} % defines the width of the characters groups
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CHANGE THIS FOR EACH EPISODE
\title{\textsc{Plans Within Plans (abridged)}}
\posttitle{\par\vskip1em{\normalfont\normalsize\scshape An Interlude\par\vfill}\end{center}}
\author{Acquisitions Incorporated: The C-Team}
\date{April 5 2018}

\Character[Jerry Holkins]{DM}{dm}

\Character[Trystan Falcone]{Trystan}{trystan} % define characters
\Character[Kate Welch]{Kate}{kate}
\Character[Kris Straub]{Kris}{kris}
\Character[Ryan Hartman]{Ryan}{ryan}

\Character[Walnut Dankgrass]{Walnut}{walnut} % define characters
\Character[Rosie Beestinger]{Rosie}{rosie} % define characters
\Character[K'thriss Drow'b]{k'thriss}{kthriss} % define characters
\Character[Donaar Blit'zen]{Donaar}{donaar} % define characters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage
\pagestyle{plain}

\settowidth{\speakswidth}{\speaksfont{K'thriss}\speaksdel\hspace{\speechskip}}
{\renewcommand{\arraystretch}{1.5}
\begin{center}
	\huge{Dramatis Personae}
\end{center}
\begin{tabular}{l l l} 
	Kris Straub & \textsc{K'thriss Drow'b} & Drow Warlock \\
\end{tabular}

\vspace{.5in}

\begin{stagedir}
	A door opens to reveal \kthriss sitting at a table in his study.
\end{stagedir}

\begin{drama}

\begin{pc}{K'Thriss}
	Oh, hello friend. I'm sorry, you'll have to
return during business hours.

I was just collecting my own thoughts
about the C-Team's recent endeavors.
Since rescuing Omin's sister from the
Wandering Crypt, we thought things might
be slowing down here around the Drawn and
Courtier. 

But then our first job arrived.
The B-Team's Oak Truestrike – maybe a pen
name devised as a child – requested
interdepartmental assistance locating
Brahma Lutier, their cartographer. 

As a pure courtesy, we traveled with Oak to
Brahma's last-known whereabouts, the town
of Westbridge, where we explored the
neglected Church of Lysander. 

But beneath the church a different kind of service
was being held. There we glimpsed Brahma,
corrupted by some force, who assailed
the party with the ex-living, and then
vanished. 

Walnut received word from the
Home Office that the B Team's exclusive
license had been revoked, and that oak
true strike was now a wanted man. We
captured him, dragging him back to Redmarch,
but he eluded us by using a quirk
of the Acquisitions Incorporated test
market system. 

We pursued, ending up in a
maddening fractal plane which led us
unexpectedly into the realm of the
Sanguilith, my patron god in protest, who
imprisoned my true deity. It was Oak who
sought to come here, paid by our rival Dran
Enterprises to do so, but the Sanguilith
trapped him in crystal along with
the other gods. 

Some errors were made in
attempting to free him, and then a couple
of amenable god-scavengers explained that
Oak's blood had been changed, turning him
into kind of a deity bait for purposes
unknown.

As we made our exit before the Sanguilith
woke, we found ourselves horribly
detoured – teleported to the Underdark, a
place I never wanted to return to. But
capricious destiny had other plans, as
our arrival was bafflingly foretold by a
dwarven king's prophecy in Alcazar.
Proving our case, we accepted an
unremarkable mithril pick from them, but
upon departing, we found the road barred
by a goblin army and an Underdark druid
known as Carver Gaul. He turned out to be
an A-okay mind flayer on a quest that
mirrored my own. My new best friend's
task required us to travel into the
blackest heart of Lolth's domain, Guallidurth, 
my birthplace and where my
tyrannical priestess mother would kill
for a chance to kill me! (for my escape)

But we were ill-equipped for the
Underdark,
even with the use of one of Gaul's goblin
supplicants, Tasty. The Home Office also
sent help in the form of a powerful
sorcerer on retainer, by the name of
Strix. She's okay, but I'm not crazy
about her methods. 

From outfitter and relic
enthusiast Moral, we acquired drow 
disguises for entry into Guallidurth – 
and they could not have been worse
disguises – but they did transmute Tasty
into Taste-full, who got a heaping helping
of that savory meat! 

Anyway, House Rah'uuthli – 
my former home – had fallen into such
disfavor that the city condemned it to
reclamation by the wilds of the
Underdark, its ruins now home to a host
of Driders, one of which had been my
mother. 

Exploring the house, I discovered
that my father's heresy closely matched
my own, and he had cleverly hidden a
fully appointed study arcanically folded
inside the blade of a knife, where he
researched That Which Endures, the god of
Carver Gaul. As we prepared to deliver
our findings, Donaar and I were slain by a
dormant member of Walnut's grove who
shared a vision of the ancient past with
Rosie and Walnut, and we learned that
Walnut's kind and mine were once mortal
enemies. Pretty small world if you think about
it.

The priestess, Nilayan, revived and armed
myself, and upon returning to the Lake of
radiant mists we were able to free That
Which Endures, who strangely consumed all the goblins
from Gaul's army, turning them into gentle
green beings, and ignored Gaul entirely!

You know, it's a lot to process. 

You're pretty much all caught up now. 

\end{pc}

\StageDir{A \textsc{Skeleton} opens the door to K'Thriss's study.}

\begin{pc}{Skeleton} I'm sorry,
	I made a mistake, I thought this was the
	toilet. This is the wrong door.
\end{pc}

\begin{pc}{K'Thriss}
	Oh, across the hall friend! Enjoy urinating!
\end{pc}

\begin{pc}{Skeleton}
	Perhaps, but if you put a sign on the
	door people would not keep making this
	mistake.
\end{pc}

\begin{pc}{K'Thriss}
	Oh, I don't mind!
\end{pc}

\end{drama}

\end{document}